---
title: "QMSS5072_HW1"
author: "Ludwig Zhao"
date: "2/3/2020"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PROJECT DESCRIPTION 

* Name: COMSCI 111 Operating Systems Principles
* Github:  [https://github.com/luxwig/CS111_design](https://github.com/luxwig/CS111_design)
* Short Description: This is a design project for CS111 OS principle, implementing a bash shell, with paralleling execution and debug/step-by-step functionality
* Created by: Jing Wu and Sichen Zhao

## PROJECT SUMMARY

* This program reads from a bash commands file and print the commands by constructing a command tree. 
* This program runs the commands as bash does
* This program parallel execuates the commands as it stated in the spec.

No major bugs are detected at this point. However, minor bugs may exsit.

### LIMITATION

* The command grammer is only limited to the subsets that is given in the spec. NO additional improvment is implemented.

* The program has limited parallel execuataion as it stated in the spec.

### FEATURES

* -x and -v function is added to output the the command for each step
* -d is added to show the step by step debug mode and interaction


## PLOT
```{r}
plot(sin, -pi, 2*pi)
```


