---
title: "Hw3"
author: "Ludwig Zhao"
date: "2/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r}
library(nycflights13)
library(dplyr)
data <- flights
```

# 1. Write a function that takes a single numerical vector and returns three values, the minimum number, the median, and the maximum number of the vector.  Test your function using the month column of the flights dataset.


```{r}
getMinMedianMax <- function(x) {
  c(min(x), median(x), max(x))
}

getMinMedianMax(data$month)
```

## 1b)  Explain your reasoning for choosing your function’s name

The method (function) uses cascalCase and begin with a verb or prefix (in this case *get*). Since the function will return min, median and max, based on abovementioned convention, it will be *get* follow by *Min*, *Median* and *Max*, with cascalCase convention.

# 2. Write a function that categorizes a numerical variable in the flights data into four categories: 

Note the output will rewrite the data in *columnName* to the desired category
```{r}
categorizeFlightData <- function(data, columnName){
    dataCat <-as.name(columnName)
    data %>%
      mutate(
        !!dataCat  := case_when (
         !!dataCat >= 500  &  !!dataCat <= 1159 ~ "Morning",
         !!dataCat >= 1200 &  !!dataCat <= 1659 ~ "Afternoon",
         !!dataCat >= 1700 &  !!dataCat <= 2059 ~ "Evening",
         !!dataCat >= 2100 |  !!dataCat <= 459 ~ "Night"
      )
     )
}


categorizeFlightData(flights, 'dep_time')
```

## 2b)  Explain your reasoning for choosing your function’s name

Similar to 1b), the method (function) uses cascalCase  and begin with a verb or prefix (in this case *categorize*). Since the function categorizes the flight data into 4 different segments, based on abovementioned convention, it will be *categorize* follow by *Flight*, *Data*, with cascalCase convention.

# 3. Write a function that calculates the median of all numeric variables in the flights dataset using a for loop.  

Note that NA is stripped if the column conatins NA
```{r}
getMedianAllNumVar <- function(){
  dataVars<-names(select_if(flights, is.numeric))
  result<-data.frame(row.names = "median")
  for (varName in dataVars){
    result[[varName]] <- median(flights[[varName]], na.rm = TRUE)
  }
  result
}

getMedianAllNumVar()
```


## 3b)  Explain your reasoning for choosing your function’s name

Similar to 1b), the method (function) uses cascalCase and begin with a verb or prefix (in this case *get*). Since the function gets median values for all numeric variables, based on abovementioned convention, it will be *get* follow by *Num* (short for numeric), *Var* (short for variables), with cascalCase convention.
