---
title: "Hw3"
author: "Ludwig Zhao"
date: "2/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r}
library(nycflights13)
library(dplyr)
data <- flights
```

# 1. Write a function that takes a single numerical vector and returns three values, the minimum number, the median, and the maximum number of the vector.  Test your function using the month column of the flights dataset.


```{r}
GetMinMedianMax <- function(x) {
  c(min(x), median(x), max(x))
}

GetMinMedianMax(data$month)
```

## 1b)  Explain your reasoning for choosing your function’s name

The method (function) is use PascalCase based on C++ style (https://google.github.io/styleguide/cppguide.html#Function_Names) and begin with a verb or prefix (under this case *Get*). Since the function will return min, median and max,  based abovementioned convention, it will be *Get* follow by *Min*, *Median* and *Max*, with first letter of each word capitalized (PascalCase).

# 2. Write a function that categorizes a numerical variable in the flights data into four categories: 


```{r}
CategorizeFlightData <- function(data, columnName){
    dataCat <- select(data, all_of(columnName))
    data %>%
      mutate(
        !!columnName  := case_when (
         dataCat >= 500  &  dataCat <= 1159 ~ "Morning",
         dataCat >= 1200 &  dataCat <= 1659 ~ "Afternoon",
         dataCat >= 1700 &  dataCat <= 2059 ~ "Evening",
         dataCat >= 2100 |  dataCat <= 459 ~ "Night"
      )
     )
}

CategorizeFlightData(flights, 'dep_time')
```

## 2b)  Explain your reasoning for choosing your function’s name

Similar to 1b), the method (function) is use PascalCase based on C++ style (https://google.github.io/styleguide/cppguide.html#Function_Names) and begin with a verb or prefix (in this case *Categorize*). Since the function categorizes the flight data into 4 different segments, based abovementioned convention, it will be *Categorize* follow by *Flight*, *Data*, with first letter of each word capitalized (PascalCase).